220410_Competition

### 2023-08-13 code/data_cleaning.Rmd
sending up some data

## Zips
locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")

@@

## Sites
locs <- paste("UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")

@@

chc <- read.csv("chc.csv")

@@

uds.6b.2012 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2013 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
uds.6b.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

@@

uds.HIT.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 0) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 2) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)

uds.HIT.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)

uds.HIT.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>%
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
uds.HIT.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "HITInformation", skip = 0) %>%
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)

@@

## Read in Covariates
```{r}
# Table 3B
uds.3B.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

@@

# Table 4
uds.4.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

uds.4.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

uds.4.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

@@

## Read in Clinical Outcomes
```{r}
uds.7.2014 <- read_excel("UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2015 <- read_excel("UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7_1", skip = 2) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2016 <- read_excel("UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

uds.7.2017 <- read_excel("UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2018 <- read_excel("UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2019 <- read_excel("UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

uds.7.2020 <- read_excel("UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2021 <- read_excel("UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

@@

## Read in my termination crosswalk to filter out closures
```{r}
chc.term <- read.csv("CHC_termination_crosswalk.csv")
staffing <- read.csv("/Users/jhm65/Research/CHC Costs/FQHC_Staffing.csv")
```

>>>>

## Zips
locs <- paste("//Users/jhm65/Dropbox/Git/UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")
uds.zip <- read_excel(locs[1], sheet = "HealthCenterZipCodes")

@@

## Sites
locs <- paste("//Users/jhm65/Dropbox/Git/UDS/UDS-", c(2014:2021), "-Full-Dataset.xlsx", sep = "")

@@

chc <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/chc.csv")

@@

uds.6b.2012 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2013 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 1) 
uds.6b.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

uds.6b.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0) 
uds.6b.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table6BClinicalmeasures", skip = 0)

@@

uds.HIT.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 0) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "EHRInformation", skip = 2) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)

uds.HIT.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)
uds.HIT.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>% 
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L2_Ca,	Tehr_L3_Ca, Tehr_L4_Ca, Tehr_L5_Ca, Tehr_L7_Ca)

uds.HIT.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "HITInformation", skip = 1) %>%
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)
uds.HIT.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "HITInformation", skip = 0) %>%
  select(GrantNumber, Tehr_L1b_Ca, Tehr_L4_Ca, Tehr_L7_Ca)

@@

## Read in Covariates
```{r}
# Table 3B
uds.3B.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table3B", skip = 2) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L8_Cd, T3b_L12_Ca) %>% rename(T3b_L26_Ca = T3b_L8_Cd)
uds.3B.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

uds.3B.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table3B", skip = 1) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)
uds.3B.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table3B", skip = 0) %>% select(GrantNumber, T3b_L1_Cb, T3b_L3_Cb, T3b_L8_Ca, T3b_L5_Cb, T3b_L26_Ca, T3b_L12_Ca)

@@

# Table 4
uds.4.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table4", skip = 2) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

uds.4.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

uds.4.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table4", skip = 1) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb) 
uds.4.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table4", skip = 0) %>% select(GrantNumber, T4_L1_Ca, T4_L2_Ca, T4_L3_Ca, T4_L4_Ca, T4_L5_Ca, T4_L16_Ca, T4_L23_Ca, T4_L12_Ca, T4_L12_Cb)

@@

## Read in Clinical Outcomes
```{r}
uds.7.2014 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2014-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2015 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2015-Full-Dataset.xlsx", sheet = "Table7_1", skip = 2) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2016 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2016-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

uds.7.2017 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2017-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2018 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2018-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2019 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2019-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

uds.7.2020 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2020-Full-Dataset.xlsx", sheet = "Table7_1", skip = 1) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c) 
uds.7.2021 <- read_excel("//Users/jhm65/Dropbox/Git/UDS/UDS-2021-Full-Dataset.xlsx", sheet = "Table7_1", skip = 0) %>% select(GrantNumber, T7_Li_C1a, T7_Li_C1b,	T7_Li_C1c,	T7_Li_C1d, T7_Li_C2a,	T7_Li_C2b,	T7_Li_C2c)

@@

## Read in my termination crosswalk to filter out closures
```{r}
chc.term <- read.csv("//Users/jhm65/Dropbox/Git/Competition/data_raw/CHC_termination_crosswalk.csv")
staffing <- read.csv("//Users/jhm65/Dropbox/Git/Data/FQHC_Staffing.csv")
```
